### 2025-11-07 multiple-regression.qmd
20251107 - suppression

>>>>

## Suppression {#sec-multipleRegressionSuppression}

Suppression in a regression model occurs when including a [predictor variable](#sec-correlationalStudy) increases the magnitude of the regression coefficient (i.e., beta) of another [predictor variable](#sec-correlationalStudy) on an [outcome variable](#sec-correlationalStudy) [@MacKinnon2000].
The suppressor variable suppresses irrelevant variance in another [predictor variable](#sec-correlationalStudy), allowing the [predictor variable's](#sec-correlationalStudy) association with the [outcome variable](#sec-correlationalStudy) to emerge more clearly.
Three types of suppression are depicted in @GaylordHarden2010.
